Evaluating Sound Similarity Metrics for Differentiable, Iterative Sound-Matching

### 2025-05-16 extra_figures/evaluation_graph.tex
Updates from Overleaf

\begin{figure*}
\resizebox{\linewidth}{!}{ % Automatically scales diagram to fit page width
\begin{tikzpicture}[
    function/.style={rectangle, draw, rounded corners, minimum width=2cm, minimum height=1cm, text centered, node distance=1cm},
    distribution/.style={ellipse, draw, minimum width=1cm, minimum height=0cm, text centered, node distance=0.3cm},
    gaussian/.style={draw, smooth, samples=100, domain=-2.5:2.5},
    NPSK/.style={rectangle, draw, rounded corners, minimum width=2.5cm, minimum height=1cm, text centered, node distance=1.5cm, fill=blue!20},
    level 1/.style={sibling distance=6cm, level distance=1cm},
    level 2/.style={sibling distance=2cm, level distance=1.2cm},
    mss/.style={fill=red!50, draw=black},
    ploss/.style={fill=blue!50, draw=black},
    likert/.style={fill=green!40, draw=black}
]

% Existing functions and distributions diagram
\node[function] {Synthesizer Program}
    child { node[function] {DTW\_Onset}
        child { node[distribution, mss] {MSS}
            child[grow=down, level distance=1.5cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[red] plot (\x/3, {exp(-\x*\x)});  % Red Gaussian
                    \end{tikzpicture}
                }
            }
        }
        child { node[distribution, ploss] {P-Loss}
            child[grow=down, level distance=1.5cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[blue] plot (\x/3, {exp(-\x*\x)});  % Blue Gaussian
                    \end{tikzpicture}
                }
            }
        }
        child { node[distribution, likert] {Likert}
            child[grow=down, level distance=1.5cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[green] plot (\x/3, {exp(-\x*\x)});  % Green Gaussian
                    \end{tikzpicture}
                }
            }
        }
    }
    child { node[function] {L1\_Spec}
        child { node[distribution, mss] {MSS} }
        child { node[distribution, ploss] {P-Loss} }
        child { node[distribution, likert] {Likert} }
    }
    child { node[function] {SIMSE\_Spec}
        child { node[distribution, mss] {MSS} }
        child { node[distribution, ploss] {P-Loss} }
        child { node[distribution, likert] {Likert} }
    }
    child { node[function] {JTFS}
        child { node[distribution, mss] {MSS}
            child[grow=down, level distance=1.5cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[red] plot (\x/3, {exp(-\x*\x)});  % Red Gaussian
                    \end{tikzpicture}
                }
            }
        }
        child { node[distribution, ploss] {P-Loss}
            child[grow=down, level distance=1.5cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[blue] plot (\x/3, {exp(-\x*\x)});  % Blue Gaussian
                    \end{tikzpicture}
                }
            }
        }
        child { node[distribution, likert] {Likert}
            child[grow=down, level distance=1.5cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[green] plot (\x/3, {exp(-\x*\x)});  % Green Gaussian
                    \end{tikzpicture}
                }
            }
        }
    };

% Label for the second row (Distributions)
\node at (0,-4) {\textbf{$\longleftarrow$\ \ \large Bootstrapped Distributions\ \ $\longrightarrow$}};
% Left side: NPSK with MSS

% Left side: NPSK with MSS
\node[NPSK, text height=5ex, align=center, fill=red!30, draw=black] at (-6,-6) {NPSK with 4 \\ MSS distributions};
\draw[->] (-6,-6.5) -- (-6,-7.5) node[below, below] {\textbf{Ranks 1-4}};
\draw[red!40, thick] (-5, -5.4) -- (-2.95, -4.95);  % Line 1
\draw[red!40, thick] (-5.5, -5.4) -- (-3.5, -4.75);  % Line 2
\draw[red!40, thick] (-6, -5.4) -- (-5.5, -4.75);  % Line 3
\draw[red!40, thick] (-6.5, -5.4) -- (-9, -4.75);    % Line 4

% Middle: NPSK with P-Loss
\node[NPSK, text height=5ex, align=center, fill=blue!40, draw=black] at (0,-6) {NPSK with 4 \\ P-Loss distributions};
\draw[->] (0,-6.5) -- (0,-7.5) node[below, below] {\textbf{Ranks 1-4}};
\draw[blue!40, thick] (1.5, -5.4) -- (3.25, -4.75);   % Line 1
\draw[blue!40, thick] (0.75, -5.4) -- (1.5, -4.75);   % Line 2
\draw[blue!40, thick] (-0.25, -5.4) -- (-1, -4.75);   % Line 3
\draw[blue!40, thick] (-0.75, -5.4) -- (-3, -4.75);   % Line 4

% Right side: NPSK with Likert
\node[NPSK, text height=5ex, align=center, fill=green!30, draw=black] at (6,-6) {NPSK with 4 \\ Likert distributions};
\draw[->] (6,-6.5) -- (6,-7.5) node[below, below] {\textbf{Ranks 1-4}};
\draw[green!50, thick] (7.5, -5.4) -- (8.75, -4.75);  % Line 1
\draw[green!50, thick] (6.75, -5.4) -- (6, -4.75);    % Line 2
\draw[green!50, thick] (5.75, -5.4) -- (4, -4.75);    % Line 3
\draw[green!50, thick] (4.95, -5.4) -- (3.25, -4.95);    % Line 4

>>>>

\begin{figure*}
\resizebox{\linewidth}{!}{ % Automatically scales diagram to fit page width
\begin{tikzpicture}[
    function/.style={rectangle, draw, rounded corners, minimum width=2cm, minimum height=1cm, text centered, node distance=1cm},
    distribution/.style={ellipse, draw, minimum width=1cm, minimum height=0cm, text centered, node distance=0.1cm},
    gaussian/.style={draw, smooth, samples=100, domain=-2.5:2.5},
    NPSK/.style={rectangle, draw, rounded corners, minimum width=2.5cm, minimum height=1cm, text centered, node distance=1.5cm, fill=blue!20},
    level 1/.style={sibling distance=6cm, level distance=1cm},
    level 2/.style={sibling distance=2cm, level distance=1.2cm},
    mss/.style={fill=red!50, draw=black},
    ploss/.style={fill=blue!50, draw=black},
    likert/.style={fill=green!40, draw=black}
]

% Existing functions and distributions diagram
\node[function] {Synthesizer Program}
    child { node[function] {DTW\_Onset}
        child { node[distribution, mss] {MSS}
            child[grow=down, level distance=1cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[red] plot (\x/3, {exp(-\x*\x)});  % Red Gaussian
                    \end{tikzpicture}
                }
            }
        }
        child { node[distribution, ploss] {P-Loss}
            child[grow=down, level distance=1cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[blue] plot (\x/3, {exp(-\x*\x)});  % Blue Gaussian
                    \end{tikzpicture}
                }
            }
        }
        child { node[distribution, likert] {Likert}
            child[grow=down, level distance=1cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[green] plot (\x/3, {exp(-\x*\x)});  % Green Gaussian
                    \end{tikzpicture}
                }
            }
        }
    }
    child { node[function] {L1\_Spec}
        child { node[distribution, mss] {MSS} }
        child { node[distribution, ploss] {P-Loss} }
        child { node[distribution, likert] {Likert} }
    }
    child { node[function] {SIMSE\_Spec}
        child { node[distribution, mss] {MSS} }
        child { node[distribution, ploss] {P-Loss} }
        child { node[distribution, likert] {Likert} }
    }
    child { node[function] {JTFS}
        child { node[distribution, mss] {MSS}
            child[grow=down, level distance=1cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[red] plot (\x/3, {exp(-\x*\x)});  % Red Gaussian
                    \end{tikzpicture}
                }
            }
        }
        child { node[distribution, ploss] {P-Loss}
            child[grow=down, level distance=1cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[blue] plot (\x/3, {exp(-\x*\x)});  % Blue Gaussian
                    \end{tikzpicture}
                }
            }
        }
        child { node[distribution, likert] {Likert}
            child[grow=down, level distance=1cm] {
                node[draw=none] {
                    \begin{tikzpicture}[scale=0.7]
                        \draw[green] plot (\x/3, {exp(-\x*\x)});  % Green Gaussian
                    \end{tikzpicture}
                }
            }
        }
    };

% Label for the second row (Distributions)
\node at (0,-3.25) {\textbf{$\longleftarrow$\ \ \large Bootstrapped Distributions\ \ $\longrightarrow$}};
% Left side: NPSK with MSS

\def\xoffsetL{-0.5}
\def\xoffsetM{0}
\def\xoffsetR{0.5}
\def\yoffset{1}

% Left: NPSK with MSS
\node[NPSK, text height=5ex, align=center, fill=red!30, draw=black] at ({-6+\xoffsetL},{-6+\yoffset}) {NPSK with 4 \\ MSS distributions};
\draw[->] ({-6+\xoffsetL},{-6.5+\yoffset}) -- ({-6+\xoffsetL},{-6.6+\yoffset}) node[below, below] {\textbf{Ranks 1-4}};
\draw[red!40, thick] ({-5+\xoffsetL}, {-5.4+\yoffset}) -- ({-2.95+\xoffsetL}, {-5.15+\yoffset});  % Line 1
\draw[red!40, thick] ({-5.5+\xoffsetL}, {-5.4+\yoffset}) -- ({-3.5+\xoffsetL}, {-4.75+\yoffset});  % Line 2
\draw[red!40, thick] ({-6+\xoffsetL}, {-5.4+\yoffset}) -- ({-5.5+\xoffsetL}, {-4.75+\yoffset});  % Line 3
\draw[red!40, thick] ({-6.5+\xoffsetL}, {-5.4+\yoffset}) -- ({-9+\xoffsetL}, {-4.75+\yoffset});  % Line 4

% Middle: NPSK with P-Loss
\node[NPSK, text height=5ex, align=center, fill=blue!40, draw=black] at ({0+\xoffsetM},{-6+\yoffset}) {NPSK with 4 \\ P-Loss distributions};
\draw[->] ({0+\xoffsetM},{-6.5+\yoffset}) -- ({0+\xoffsetM},{-6.6+\yoffset}) node[below, below] {\textbf{Ranks 1-4}};
\draw[blue!40, thick] ({1.5+\xoffsetM}, {-5.4+\yoffset}) -- ({3.25+\xoffsetM}, {-4.75+\yoffset});  % Line 1
\draw[blue!40, thick] ({0.75+\xoffsetM}, {-5.4+\yoffset}) -- ({1.5+\xoffsetM}, {-4.75+\yoffset});  % Line 2
\draw[blue!40, thick] ({-0.25+\xoffsetM}, {-5.4+\yoffset}) -- ({-1+\xoffsetM}, {-4.75+\yoffset});  % Line 3
\draw[blue!40, thick] ({-0.75+\xoffsetM}, {-5.4+\yoffset}) -- ({-3+\xoffsetM}, {-4.75+\yoffset});  % Line 4

% Right: NPSK with Likert
\node[NPSK, text height=5ex, align=center, fill=green!30, draw=black] at ({6+\xoffsetR},{-6+\yoffset}) {NPSK with 4 \\ Likert distributions};
\draw[->] ({6+\xoffsetR},{-6.5+\yoffset}) -- ({6+\xoffsetR},{-6.6+\yoffset}) node[below, below] {\textbf{Ranks 1-4}};
\draw[green!50, thick] ({7.5+\xoffsetR}, {-5.4+\yoffset}) -- ({8.75+\xoffsetR}, {-5+\yoffset});  % Line 1
\draw[green!50, thick] ({6.75+\xoffsetR}, {-5.4+\yoffset}) -- ({6+\xoffsetR}, {-4.75+\yoffset});    % Line 2
\draw[green!50, thick] ({5.75+\xoffsetR}, {-5.4+\yoffset}) -- ({4+\xoffsetR}, {-4.85+\yoffset});    % Line 3
\draw[green!50, thick] ({4.95+\xoffsetR}, {-5.4+\yoffset}) -- ({3.25+\xoffsetR}, {-5.1+\yoffset}); % Line 4

### 2025-05-16 main.tex
Updates from Overleaf

Automatic sound design has been a subject of research for decades, with reduction of tinkering time and creation of ``interesting" sounds as the main motivators \cite{krekovic2019insights,turian2020sorry,horner1993machine,salimi2020make,esling2019flow,engel2020ddsp,mitchell2007evolutionary,shier2020spiegelib}. \textit{Sound-matching} is a common form of automatic sound design explored in literature, where a similarity metric (or loss function) is given, and the goal is to find parameters for a synthesizer that replicate \textit{all} or \textit{some} of the characteristics of a target sound as best as possible~\cite{horner1993machine,mitchell2007evolutionary}. Our analysis of past works shows that this general goal of ``sound-matching'' can be broken down in to very different subtypes, many of them rarely or never explored, despite their relevance to practical applications. This leads us to a typology of sound-matching tasks, and the importance of \textit{differentiable, iterative sound-matching}, rarely explored in previous literature~\cite{vahidi2023mesostructures}.

@@

Despite the early popularity of the iterative approach~\cite{justice1979analytic,horner1993machine,mitchell2007evolutionary}, recent works in sound-matching have favored supervised learning using inference models, deep neural-networks (\gls{DNNs}), and large datasets. Rather than continually interacting with the environment, these models learn from a dataset of inputs (synthesizer parameters) and outputs (corresponding sound), and predict the synthesizer parameters for new sounds~\cite{yee2018automatic,han2023perceptual,han2024learning}.

@@

Here we discuss four methods of audio representation and the corresponding loss functions. Three of which have been used in previous works, and a novel method which we will make use of in our own experiments.

@@

Masuda \textit{et al.} also applied supervised learning to synthesizer parameter estimation~\cite{masuda2021soundmatch}. Their work highlights the issue of non-linearity in parameter-to-synthesizer outputs and out-of-domain search. This work uses a differentiable subtractive synthesizer (two oscillators and an LP filter). A NN model was pre-trained using an in-domain dataset of randomly selected parameters and P-Loss. After training, the model was fine-tuned using 20,000 out-of-domain sounds from the NSynth dataset~\cite{engel2017neural} and multi-scale spectrogram loss~\cite{engel2020ddsp}. This approach proved more effective---that is, lower multi-level spectral difference in out-of-domain tests---than baseline models, which were either not exposed to out-of-domain sounds or trained exclusively with P-Loss. Subjective hearing tests were conducted, showing a preference for the fine-tuned model~\cite{masuda2021soundmatch}.

@@

Uzrad \textit{et al.}~\cite{uzrad2024diffmoog} took another unique approach to sound-matching: using a differentiable \textit{synthesis chain} of DSP generators and effects and a loss function that combines P-Loss with a \textit{signal-chain loss}. The synthesizer is a customizable chain of effects, which feed one output as input to the next step of the chain; signal-chain loss compares the parameter and output difference at every output step in the chain~\cite{uzrad2024diffmoog}. Possible chain functionalities are FM/AM, Low Frequency Oscillators (\gls{LFO}), filters, and envelopes. Like the results shown by Masuda \textit{et al.}~\cite{masuda2021soundmatch}, better out-of-domain results were achieved when pre-trained on in-domain data and fine-tuned using out-of-domain NSynth data~\cite{engel2017neural}.

@@

We test four different loss functions and compare their success in sound-matching using four different synthesizers. We verify the success of the sound-matching process using two automatic measures of sound similarity (MSS and P-Loss) and a manual blinded hearing test conducted by two of the authors where likert scores~\cite{jebb2021review} of 1-5 are assigned to a subset of final outputs and the corresponding targets.

An \textit{experiment} is one iteration of sound-matching given a loss function, target sound,
and synthesizer program. When the final iteration is complete, a score is given (automatically with an algorithm or with manual listening) to an experiment that measures its success in replicating the target sound. Consider the following simplified scenario: we have two loss functions, $L_1$ and $L_2$, and a single synthesizer program $P$ with a target parameter set $\theta^*$ where the target sound is $t$, or $P(\theta^*) = t$. We run a large number (in this case, 300 for each loss function) of experiments where we randomly set the initial ($\theta_0$) and target parameters ($\theta^*$) of $P$ and run an iterative sound-matching loop for each loss function, with max number of iterations set to 200. When the loop is terminated, we measure the similarity of the final output sound $x$ (where $P(\theta_{199}) = x$) to $t$, or if using P-Loss we compare $\theta_{199}$ to $\theta^*$. Having 300 experiments gives us a distribution of losses to determine whether $L_1$ or $L_2$ led to better performance. This simplified example leads us to our methodology which has four loss functions, four synthesizer programs, and three different evaluation methods of scoring sound similarity.

@@

Automatic sound evaluation methods are often unreliable, as their alignment with the subjective judgments of human listeners is uncertain. Therefore, listening tests are conducted by randomly sampling 40 experiment results for each program and loss function pair. Two of the authors then assign blinded similarity scores to the outputs and targets using a 5-point Likert scale (1 = no similarity, 5 = near identical)~\cite{jebb2021review}. Using Spearmna's rank correlation~\cite{spearman1987proof,rebekic2015pearson}, we found a very strong rate of agreement between the human listeners (see Section~\ref{sec:consistency_in_rankings}), a good indicator that the scores assigned by manual listeners can be treated as the ground truth. We then combine the ranks assigned by both authors, giving us 80 ranks per program and loss function pair.

@@

\textbf{Weaknesses:} Compared to previous work, we presented a more cohesive approach to iterative sound-matching which utilizes a variety of loss functions and synthesis methods. However, there are many other methods of synthesis and sound-similarity that can be combined in practically infinite ways.

To limit the scope of our experiments, we had no choice but to use arbitrary parameters for the various signal processing functions. We used bare-bones versions of STFT and JTFS with fixed parameters. We did not test complex synthesizers using parallel and sequential DSP functions. Arbitrary hyperparameters such as learning rate and max number of iterations were selected for the DL pipeline, and only the RMSProp optimizer was tested.

>>>>

Automatic sound design has been a subject of research for decades, with reduction of tinkering time and creation of ``interesting" sounds as the main motivators \cite{krekovic2019insights,turian2020sorry,horner1993machine,salimi2020make,esling2019flow,engel2020ddsp,mitchell2007evolutionary,shier2020spiegelib,masuda2021soundmatch,masuda2023improving}. \textit{Sound-matching} is a common form of automatic sound design explored in literature, where a similarity metric (or loss function) is given, and the goal is to find parameters for a synthesizer that replicate \textit{all} or \textit{some} of the characteristics of a target sound as best as possible~\cite{horner1993machine,mitchell2007evolutionary,masuda2023improving}. Our analysis of past works shows that this general goal of ``sound-matching'' can be broken down in to very different subtypes, many of them rarely or never explored, despite their relevance to practical applications. This leads us to a typology of sound-matching tasks, and the importance of \textit{differentiable, iterative sound-matching}, rarely explored in previous literature~\cite{vahidi2023mesostructures}.

@@

Despite the early popularity of the iterative approach~\cite{justice1979analytic,horner1993machine,mitchell2007evolutionary}, recent works in sound-matching have favored supervised learning using inference models, deep neural-networks (\gls{DNNs}), and large datasets. Rather than continually interacting with the environment, these models learn from a dataset of inputs (synthesizer parameters) and outputs (corresponding sound), and predict the synthesizer parameters for new sounds~\cite{yee2018automatic,han2023perceptual,han2024learning,masuda2021soundmatch,masuda2023improving}.

@@

Here we discuss four methods of audio representation and the corresponding loss functions. Three of which have been used in previous works, and a novel method not previously used in iterative sound-matching.

@@

Masuda \textit{et al.} also applied supervised learning to synthesizer parameter estimation~\cite{masuda2021soundmatch}. Their work highlights the issue of non-linearity in parameter-to-synthesizer outputs and out-of-domain search. This work uses a differentiable subtractive synthesizer (two oscillators and an LP filter). A NN model was pre-trained using an in-domain dataset of randomly selected parameters and P-Loss. After training, the model was fine-tuned using 20,000 out-of-domain sounds from the NSynth dataset~\cite{engel2017neural} and multi-scale spectrogram loss~\cite{engel2020ddsp}. This approach proved more effective---that is, lower multi-level spectral difference in out-of-domain tests---than baseline models, which were either not exposed to out-of-domain sounds or trained exclusively with P-Loss. Subjective hearing tests were conducted, showing a preference for the fine-tuned model~\cite{masuda2021soundmatch}. Masuda \textit{et al.} later extended this work with semi-supervised learning, highlighting significant gaps in in-domain and out-of-domain performance~\cite{masuda2023improving}.

@@

Uzrad \textit{et al.}~\cite{uzrad2024diffmoog} took another unique approach to sound-matching: using a differentiable \textit{synthesis chain} of DSP generators and effects and a loss function that combines P-Loss with a \textit{signal-chain loss}. The synthesizer is a customizable chain of effects, which feed one output as input to the next step of the chain; signal-chain loss compares the parameter and output difference at every output step in the chain~\cite{uzrad2024diffmoog}. Possible chain functionalities are FM/AM, Low-Frequency Oscillators (\gls{LFO}), filters, and envelopes. Like the results shown by Masuda \textit{et al.}~\cite{masuda2021soundmatch}, better out-of-domain results were achieved when pre-trained on in-domain data and fine-tuned using out-of-domain NSynth data~\cite{engel2017neural}.

@@

We test four different loss functions and compare their success in sound-matching using four different synthesizers. We verify the success of the sound-matching process using two automatic measures of sound similarity (MSS and P-Loss) and a manual blinded hearing test conducted by two of the authors where Likert scores~\cite{jebb2021review} of 1-5 are assigned to a subset of final outputs and the corresponding targets.

An \textit{experiment} is one iteration of sound-matching given a loss function, target sound,
and synthesizer program. When the final iteration is complete, a score is given (automatically with an algorithm or with manual listening) to an experiment that measures its success in replicating the target sound. Consider the following simplified scenario: we have two loss functions, $L_1$ and $L_2$, and a single synthesizer program $P$ with a target parameter set $\theta^*$ where the target sound is $t$, or $P(\theta^*) = t$. We run a large number (in this case, 300 for each loss function) of experiments where we randomly set the initial ($\theta_0$) and target parameters ($\theta^*$) of $P$ and run an iterative sound-matching loop for each loss function, with maximum number of iterations set to 200. When the loop is terminated, we measure the similarity of the final output sound $x$ (where $P(\theta_{199}) = x$) to $t$, or if using P-Loss we compare $\theta_{199}$ to $\theta^*$. Having 300 experiments gives us a distribution of losses to determine whether $L_1$ or $L_2$ led to better performance. This simplified example leads us to our methodology which has four loss functions, four synthesizer programs, and three different evaluation methods of scoring sound similarity.

@@

Automatic sound evaluation methods are often unreliable, as their alignment with the subjective judgments of human listeners is uncertain. Therefore, listening tests are conducted by randomly sampling 40 experiment results for each program and loss function pair. Two of the authors then assign blinded similarity scores to the outputs and targets using a 5-point Likert scale (1 = no similarity, 5 = near identical)~\cite{jebb2021review}. Using Spearman's rank correlation~\cite{spearman1987proof,rebekic2015pearson}, we found a very strong rate of agreement between the human listeners (see Section~\ref{sec:consistency_in_rankings}), a good indicator that the scores assigned by manual listeners can be treated as the ground truth. We then combine the ranks assigned by both authors, giving us 80 ranks per program and loss function pair.

@@

\textbf{Weaknesses:} 
While cannot prove that a universally best similarity measure does not exist, we can advocate for more creativity in the field based on our findings. Compared to previous work, we presented a more cohesive approach to iterative sound-matching which utilizes a variety of loss functions and synthesis methods. However, there are many other methods of synthesis and sound-similarity that can be combined in practically infinite ways. Due to this large search space, we set arbitrary parameters for the various signal processing functions. We used bare-bones versions of STFT and JTFS with fixed parameters. We did not test complex synthesizers using parallel and sequential DSP functions. Arbitrary hyperparameters such as learning rate and max number of iterations were selected for the DL pipeline, and only the RMSProp optimizer was tested.
